Open-source tools in R for landscape ecology

### 2021-01-08 paper/paper.Rmd
Fix some minor typos

---
title: Open-source tools in R for landscape ecology
# subtitle: Do you have a subtitle? If so, write it here
# titlerunning: Open source landscape ecology tools
# authorrunning: Short form of author list if too long for running head
# thanks: |
#    Grants or other notes about the article that should go on the front
#    page should be placed here. General acknowledgments should be placed at the
#    end of the article.
authors: 
- name: Maximillian H.K. Hesselbarth
  address:
    Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
    Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, 48109, USA
  email: mhk.hesselbarth@gmail.com
- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com
- name: Johannes Signer
  address: Wildlife Sciences, Faculty of Forestry and Forest Ecology, University of Goettingen, Büsgenweg 3, 37077 Göttingen, Germany
  email: jsigner@uni-goettingen.de
- name: Laura J. Graham
  address: Geography, Earth & Environmental Sciences, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom
  email: l.graham@bham.ac.uk
keywords:
- spatial data
- statistical programming language
- R packages
- reproducibility
- ...
abstract: |
  max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
bibliography: bibliography.bib
bibstyle: spphys # bibstyle options spbasic(default), spphys, spmpsci
preamble: |
  \usepackage{caption}
  \usepackage{tabularx}
  \usepackage{multirow}
  \usepackage{placeins}
  \usepackage[modulo]{lineno}
output:
  bookdown::pdf_book:
    base_format: rticles::springer_article
    number_sections: yes
    citation_package: default
editor_options:
  chunk_output_type: console
  markdown:
    wrap: sentence
---

@@

To better understand how the landscape ecology community uses* R*, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by `r n_people` participants, of which the the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%).
Other, less frequent answers were "Data scientists", "None of the above", "Government employees" "Master's degree student" and "Bachelor's degree student" (in decreasing order).

@@

MHKH and JN are authors of the *landscapemetrics* and *landscapetools* package.
JN is author of *belg* and *motif* package. JS is author of the *amt* package. 
<!-- MH: I wasn't sure if we need to list this here, but it kind of felt like a not completely stupid idea. What do you think? -->
<!-- JS: I don't think its critical, but surely it doesn't do any arm listing this here -->

@@

MHKH and JN designed the survey form and analyzed the responses of the participants.
MHKH and JN drafted the manuscript and all authors contributed critically to the manuscript and gave final approval for publication.
We used the 'sequence--determines--credit' approach (SDC) for the sequence of authors.

>>>>

---
title: Open-source tools in R for landscape ecology
# subtitle: Do you have a subtitle? If so, write it here
# titlerunning: Open source landscape ecology tools
# authorrunning: Short form of author list if too long for running head
# thanks: |
#    Grants or other notes about the article that should go on the front
#    page should be placed here. General acknowledgments should be placed at the
#    end of the article.
authors: 
- name: Maximillian H.K. Hesselbarth
  address:
    a) Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany
    b) Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, 48109, USA
  email: mhk.hesselbarth@gmail.com
- name: Jakub Nowosad
  address: Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland
  email: nowosad.jakub@gmail.com
- name: Johannes Signer
  address: Wildlife Sciences, Faculty of Forestry and Forest Ecology, University of Goettingen, Büsgenweg 3, 37077 Göttingen, Germany
  email: jsigner@uni-goettingen.de
- name: Laura J. Graham
  address: Geography, Earth & Environmental Sciences, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom
  email: l.graham@bham.ac.uk
keywords:
- spatial data
- statistical programming language
- R packages
- reproducibility
- ...
abstract: |
  max. (200 words) Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract Abstract
bibliography: bibliography.bib
bibstyle: spphys # bibstyle options spbasic(default), spphys, spmpsci
preamble: |
  \usepackage{caption}
  \usepackage{tabularx}
  \usepackage{multirow}
  \usepackage{placeins}
  \usepackage[modulo]{lineno}
output:
  bookdown::pdf_book:
    base_format: rticles::springer_article
    number_sections: yes
    citation_package: default
editor_options:
  chunk_output_type: console
  markdown:
    wrap: sentence
---

@@

To better understand how the landscape ecology community uses *R*, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by `r n_people` participants, of which the the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%).
Other, less frequent answers were "Data scientists", "None of the above", "Government employees" "Master's degree student" and "Bachelor's degree student" (in decreasing order).

@@

MHKH and JN are authors of the *landscapemetrics* and *landscapetools* package.
JN is author of *belg* and *motif* package. JS is author of the *amt* package. LJG is author of the *grainchanger* package.
<!-- MH: I wasn't sure if we need to list this here, but it kind of felt like a not completely stupid idea. What do you think? -->
<!-- JS: I don't think its critical, but surely it doesn't do any arm listing this here -->

@@

MHKH and JN designed the survey form and analyzed the responses of the participants.
MHKH and JN drafted the manuscript with contributions of JS and LJG and all authors contributed critically to the manuscript and gave final approval for publication.
We used the 'sequence--determines--credit' approach (SDC) for the sequence of authors.

### 2021-01-08 paper/paper.tex
Fix some minor typos

\institute{
        Maximillian H.K. Hesselbarth \at
     Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, 48109, USA \\
     \email{\href{mailto:mhk.hesselbarth@gmail.com}{\nolinkurl{mhk.hesselbarth@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jakub Nowosad \at
     Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland \\
     \email{\href{mailto:nowosad.jakub@gmail.com}{\nolinkurl{nowosad.jakub@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Johannes Signer \at
     Wildlife Sciences, Faculty of Forestry and Forest Ecology, University of Goettingen, Büsgenweg 3, 37077 Göttingen, Germany \\
     \email{\href{mailto:jsigner@uni-goettingen.de}{\nolinkurl{jsigner@uni-goettingen.de}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Laura J. Graham \at
     Geography, Earth \& Environmental Sciences, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom \\
     \email{\href{mailto:l.graham@bham.ac.uk}{\nolinkurl{l.graham@bham.ac.uk}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

To better understand how the landscape ecology community uses* R*, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by 103 participants, of which the the majority were either ``PhD students'' (34\%), followed by ``Post-Docs'' (28.2\%) and ``Professors'' (12.6\%).
Other, less frequent answers were ``Data scientists'', ``None of the above'', ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

MHKH and JN are authors of the \emph{landscapemetrics} and \emph{landscapetools} package.
JN is author of \emph{belg} and \emph{motif} package. JS is author of the \emph{amt} package.

@@

MHKH and JN designed the survey form and analyzed the responses of the participants.
MHKH and JN drafted the manuscript and all authors contributed critically to the manuscript and gave final approval for publication.
We used the `sequence--determines--credit' approach (SDC) for the sequence of authors.

>>>>

\institute{
        Maximillian H.K. Hesselbarth \at
     a) Department of Ecosystem Modelling, University of Goettingen, Buesgenweg 4, 37077 Goettingen, Germany b) Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, 48109, USA \\
     \email{\href{mailto:mhk.hesselbarth@gmail.com}{\nolinkurl{mhk.hesselbarth@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jakub Nowosad \at
     Institute of Geoecology and Geoinformation, Adam Mickiewicz University, Krygowskiego 10, 61-680 Poznan, Poland \\
     \email{\href{mailto:nowosad.jakub@gmail.com}{\nolinkurl{nowosad.jakub@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Johannes Signer \at
     Wildlife Sciences, Faculty of Forestry and Forest Ecology, University of Goettingen, Büsgenweg 3, 37077 Göttingen, Germany \\
     \email{\href{mailto:jsigner@uni-goettingen.de}{\nolinkurl{jsigner@uni-goettingen.de}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Laura J. Graham \at
     Geography, Earth \& Environmental Sciences, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom \\
     \email{\href{mailto:l.graham@bham.ac.uk}{\nolinkurl{l.graham@bham.ac.uk}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

@@

To better understand how the landscape ecology community uses \emph{R}, we conducted a short survey and used mailing lists and social media to reach the community.
In total, the survey was answered by 103 participants, of which the the majority were either ``PhD students'' (34\%), followed by ``Post-Docs'' (28.2\%) and ``Professors'' (12.6\%).
Other, less frequent answers were ``Data scientists'', ``None of the above'', ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

MHKH and JN are authors of the \emph{landscapemetrics} and \emph{landscapetools} package.
JN is author of \emph{belg} and \emph{motif} package. JS is author of the \emph{amt} package. LJG is author of the \emph{grainchanger} package.

@@

MHKH and JN designed the survey form and analyzed the responses of the participants.
MHKH and JN drafted the manuscript with contributions of JS and LJG and all authors contributed critically to the manuscript and gave final approval for publication.
We used the `sequence--determines--credit' approach (SDC) for the sequence of authors.
